Creating optimal conditions for reproducible data analysis in R with \pkg{fertile}

### 2020-01-03 fertile_sdss.Rnw
added examples; #1

Much of the discussion around reproducibility is also generalized---it is written to be applicable to users working with a variety of statistical software programs. Since all statistical software programs operate differently, generalized recommendations on reproducibility are often shallow and unspecific. While they provide useful guidelines, they can often be difficult to implement, particularly to new analysts who are unsure how to apply such recommendations within the software programs they are using.
Thus, reproducibility recommendations tailored to specific software programs are more likely to be adopted. 
In this paper, we focus on reproducibility in the R programming language with a concentration on projects that use the RStudio integrated development environment.
R is an ideal candidate for reproducibility recommendations due to the language's popularity for statistical analyses and the ease with which analysts can download and begin using the software.

@@

@@

@@

@@

@@

>>>>

Much of the discussion around reproducibility is also generalized---it is written to be applicable to users working with a variety of statistical software programs. Since all statistical software programs operate differently, generalized recommendations on reproducibility are often shallow and unspecific. While they provide useful guidelines, they can often be difficult to implement, particularly to new analysts who are unsure how to apply such recommendations within the software programs they are using.
Thus, reproducibility recommendations tailored to specific software programs are more likely to be adopted.

In this paper, we focus on reproducibility in the R programming language with a concentration on projects that use the RStudio integrated development environment.
R is an ideal candidate for reproducibility recommendations due to the language's popularity for statistical analyses and the ease with which analysts can download and begin using the software.

\section{Methods}

@@

\pkg{fertile} is available for download at \url{https://github.com/baumer-lab/fertile}.

\section{Results}

@@

<<message=FALSE>>=
library(tidyverse)
library(fertile)
is_path_portable(".")
is_path_portable("~")
@

@@

<<include=FALSE>>=
readr::write_csv(mtcars, "~/Desktop/my_data.csv")
@

<<>>=
file.exists("~/Desktop/my_data.csv")
read.csv("~/Desktop/my_data.csv")
@

@@

<<message=FALSE>>=
check_some(".", contains("paths"))
@

@@

\section{Conclusion}

\pkg{fertile} is an R package that lowers barriers to reproducible data analysis projects in R.
